---
title: "Sectoral balances charts"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r Source data, echo=FALSE, message=FALSE, warning=FALSE}
#source("sectors.r")
load("sectors.rda")
```

Last updated: `r format(last.updated, "%Y-%m-%d %H:%m %Z")`

# Euro Area

```{r Euro area, echo=FALSE, message=FALSE, warning=FALSE}
plotly.list[["EA19_Q_eurostat"]]
```

Download image: [PNG](charts/EA19_Q_eurostat.png), [PDF](charts/EA19_Q_eurostat.pdf)


# France

```{r France, echo=FALSE, message=FALSE, warning=FALSE}
plotly.list[["FR_Q_eurostat"]]
```

Download image: [PNG](charts/FR_Q_eurostat.png), [PDF](charts/FR_Q_eurostat.pdf)


# Germany

```{r Germany, echo=FALSE, message=FALSE, warning=FALSE}
plotly.list[["DE_Q_eurostat"]]
```

Download image: [PNG](charts/DE_Q_eurostat.png), [PDF](charts/DE_Q_eurostat.pdf)


# Greece

```{r Greece, echo=FALSE, message=FALSE, warning=FALSE}
plotly.list[["GR_Q_eurostat"]]
```

Download image: [PNG](charts/GR_Q_eurostat.png), [PDF](charts/GR_Q_eurostat.pdf)


# Italy

```{r Italy, echo=FALSE, message=FALSE, warning=FALSE}
plotly.list[["IT_Q_eurostat"]]
```

Download image: [PNG](charts/IT_Q_eurostat.png), [PDF](charts/IT_Q_eurostat.pdf)


# Spain

```{r Spain, echo=FALSE, message=FALSE, warning=FALSE}
plotly.list[["ES_Q_eurostat"]]
```

Download image: [PNG](charts/ES_Q_eurostat.png), [PDF](charts/ES_Q_eurostat.pdf)


# Australia

```{r Australia, echo=FALSE, message=FALSE, warning=FALSE}
plotly.list[["AU_A_oecd"]]
```

Download image: [PNG](charts/AU_A_oecd.png), [PDF](charts/AU_A_oecd.pdf)

  
# China

```{r China, echo=FALSE, message=FALSE, warning=FALSE}
plotly.list[["CN_A_oecd"]]
```

Download image: [PNG](charts/CN_A_oecd.png), [PDF](charts/CN_A_oecd.pdf)


# Japan

```{r Japan, echo=FALSE, message=FALSE, warning=FALSE}
plotly.list[["JP_Q_boj_cao"]]
```

Download image: [PNG](charts/JP_Q_boj_cao.png), [PDF](charts/JP_Q_boj_cao.pdf)


# Sweden

```{r Sweden, echo=FALSE, message=FALSE, warning=FALSE}
plotly.list[["SE_Q_eurostat"]]
```

Download image: [PNG](charts/SE_Q_eurostat.png), [PDF](charts/SE_Q_eurostat.pdf)


# United Kingdom

```{r UK, echo=FALSE, message=FALSE, warning=FALSE}
plotly.list[["GB_Q_eurostat"]]
```

Download image: [PNG](charts/GB_Q_eurostat.png), [PDF](charts/GB_Q_eurostat.pdf)


# United States

```{r US, echo=FALSE, message=FALSE, warning=FALSE}
plotly.list[["US_Q_fred"]]
```

Download image: [PNG](charts/US_Q_fred.png), [PDF](charts/US_Q_fred.pdf)
